Sustainable computational science:\\ the ReScience initiative

### 2017-11-08 replies_to_reviewers.md

We thank the reviewer for the in-depth examination of our work and for his useful suggestions for the future evolution of ReScience.

Concerning what the reviewer calls a defeatist attitude towards computational reproducibility, that is not at all how we see our approach. The manuscript focuses on reporting our experiences with ReScience. Concerning reproducibility, we note that having it verified by reviewers is not sufficient. We are not aware of any practical experience demonstrating that some other approach is efficient, which is why we consider the reproducibility of software environments an unsolved problem. Many ideas are being explored at the moment, including containerization as the reviewer mentions. The effectiveness of these ideas cannot be judged yet. Nobody knows, for example, if five years from now, the then-current version Docker will still be able to handle today's container images. We see our attitude not as defeatist, but as prudent. Many of the authors are contributing to the development and evaluation of new ideas, and we will certainly try some of them out in the context of ReScience.

We have reworded some of our statements to make clearer that our doubts about reproducibility apply only to today's state of the start. We have also added a new paragraph on the reproducibility of software environments to the Outlook section.

We have corrected our description of the Github pricing model, referring to public projects rather than Open Source projects.

We have also added a sentence stating that replication authors should base their work exclusively on the contents of the original article. In practice, we have not yet encountered a case where code for the original article was available.

### 2017-11-08 draft.tex
Correct description of the Github pricing model
In reply to reviewer #1
What replication authors are allowed to use
In reply to reviewer #1

Since independent implementation is a major feature of replication
work, ReScience does not allow authors to submit replications of their
own research, nor the research of close collaborators. Mistakes in the
implementation of computational models and methods are often due to
biases that authors invariably have, consciously or not. Such biases
will inevitably carry over to a replication. Perhaps even more
importantly, cross-fertilization is generally useful in research, and
trying to replicate the work of one’s peers might pave the way for a
future collaboration, or may give rise to new ideas as a result of the
replication effort.

@@

\href{http://github.com/}{GitHub} is a commercial platform for collaborative
software development based on the popular version control system
\href{https://git-scm.com/}{git}. It offers unlimited free use to Open Source
projects, defined as projects whose contents are accessible to everyone. All
ReScience activities are organized around a few such Open Source projects
hosted by GitHub. This is an unusual choice for a scientific journal, the only
other journal hosted on GitHub being The Journal of Open Source
Software\citep{Smith:2017}. In this section, we discuss the advantages and
problems resulting from this choice, considering both technical and social
issues.

>>>>

Since independent implementation is a major feature of replication
work, ReScience does not allow authors to submit replications of their
own research, nor the research of close collaborators. Moreover,
replication work should be based exclusively on the originally
published paper, although exceptions are admitted if properly documented
in the replication article. Mistakes in the
implementation of computational models and methods are often due to
biases that authors invariably have, consciously or not. Such biases
will inevitably carry over to a replication. Perhaps even more
importantly, cross-fertilization is generally useful in research, and
trying to replicate the work of one’s peers might pave the way for a
future collaboration, or may give rise to new ideas as a result of the
replication effort.

@@

\href{http://github.com/}{GitHub} is a commercial platform for collaborative
software development based on the popular version control system
\href{https://git-scm.com/}{git}. It offers unlimited free use to public
projects, defined as projects whose contents are accessible to everyone. All
ReScience activities are organized around a few such Open Source projects
hosted by GitHub. This is an unusual choice for a scientific journal, the only
other journal hosted on GitHub being The Journal of Open Source
Software\citep{Smith:2017}. In this section, we discuss the advantages and
problems resulting from this choice, considering both technical and social
issues.
